---
title: Southwestern Michigan College Internship Technical Assessment
---

## Provide a summary of the dataset.

Include:

1.  Number of records

2.  Number of variables

3.  Variable Types

4.  Missing value counts

5.  Descriptive Statistics for numeric variables

```{r}

```

## Data Quality Issues

Identify at least five data quality issues found in the dataset. Describe the issues, explain why its a problem, and recommend a solution.

```{r}

```

## Duplicate and Integrity Checks

Determine if any duplicate records exists. Document your code and findings.

```{r}

```

## Cleaning Strategy

Describe what methods you would take to clean this dataset so it can be used for reporting and analytics.

```{r}

```

## Build a Cleaning Pipeline

1)  Create code that transform this raw data into analysis-ready dataset.
2)  Should be able to be reused if another spreadsheet with the same columns is uploaded.
3)  Include a step splitting Course into a Subject and a Course Number field.

```{r}

```

## What Else?

Are there any features that you believe could be helpful if they were included? Explain your answers.

```{r}

```

## If you are only interested in Internship 2 please skip to 'Create a Data Dictionary'. If not continue working through the notebook.

## Exploratory Analysis

Provide your own analysis of the dataset. Show charts that may be helpful to explain the dataset.

Answer questions such as:

1)  Which courses are consistently filled?
2)  Which courses are under filled?
3)  Which instructional mode has the most students?
4)  Which student populations drive enrollment?

```{r}

```

## DFW Analysis

How does the DFW rate vary across:

1)  Courses
2)  Gateway Courses
3)  Instructional Mode
4)  Student Type

```{r}

```

## Enrollment Drivers

What factors appear to be more important in explaining course enrollment? Show how you got your answers.

```{r}

```

## Build an Enrollment Planning Framework

Develop a methodology that Senior Leadership could use to determine the appropriate number of seats to offer for a course

```{r}

```

## Scenario Analysis

Evaluate these 2 Scenarios:

**Scenario A** Increase average section capacity by 10% What happens? Does this make sense for all courses?

**Scenario B** Reduce sections with fill rates below 50% What happens? What problems could this create?

```{r}

```

## Executive Recommendation

Prepare a summary for Senior Leadership

Address:

1.  Key findings

2.  Recommend planning framework

3.  Important assumptions

4.  Risks and limitations

5.  Future data needed/Data that would help predict more

```{r}

```

## Create a Data Dictionary

Create documentation describing each field used in your cleaned dataset.

```{r}

```

## Recommendations

What fixes would you suggest to prevent future data quality issues at the source?

```{r}

```
